Output Summary

### 2023-07-06 03-post-process/output-plots-children/03a-pp-checks.Rmd

# pre-spawn survival
new = post_subset(post, "x_carcass_spawned_new_dev", TRUE)
obs = post_subset(post, "x_carcass_spawned_dev", TRUE)
bp = array_format(colMeans(obs > new))
dimnames(bp) = list(all_yrs[1:dim(bp)[1]], pops)
x_carcass_spawned_bp = data.frame(
  name = rep("Prespawn", 4), pop = pops,
  origin = rep("Combined", 4), LH_type = rep("Combined", 4),
  summarize_bp(bp)
)
rownames(x_carcass_spawned_bp) = NULL

@@

### COMBINE INTO ONE TABLE ###
bp_tab = rbind(
  Pa_bp, Mb_bp, Ra_bp,
  phi_Pb_Ma_bp, phi_Pa_Ma_bp, phi_Mb_Ma_bp,
  phi_Ma_O0_bp, L_Pb_bp, L_Mb_bp, x_Ra_bp, x_Sa_prime_bp, x_carcass_spawned_bp, x_LGR_bp
)

>>>>

@@

### COMBINE INTO ONE TABLE ###
bp_tab = rbind(
  Pa_bp, Mb_bp, Ra_bp,
  phi_Pb_Ma_bp, phi_Pa_Ma_bp, phi_Mb_Ma_bp,
  phi_Ma_O0_bp, L_Pb_bp, L_Mb_bp, x_Ra_bp, x_Sa_prime_bp, x_LGR_bp
)

### 2023-07-06 03-post-process/output-plots-children/12-param-summaries.Rmd

```{r yr1-ocean-bxp2, fig.width = p3_width, fig.height = p3_height}
mypar(mfrow = c(1,3), mar = bp_mar, oma = bp_oma)
my_boxplot("sig_Lphi_O0_O1[", ylab = "Process SD", ylim = c(0,2))
my_boxplot(sub_index("kappa_phi_O0_O1[pop]", pop = "."), ylab = "Autocorrelation", ylim = c(-1,1)); ref_line(h = 0)
my_boxplot(paste0("rho_Lphi_O0_O1", vcov_inds), ticklabs = vcov_labels, ylab = "Correlation", ylim = c(-1,1)); ref_line(h = 0)
```

@@

## Pre-spawn Survival

```{r prespawn-surv-bxp, fig.width = p4_width, fig.height = p4_height, out.width = "50%"}
mypar(mfrow = c(1,3), mar = bp_mar, oma = bp_oma)
my_boxplot("mu_phi_Sb_Sa", "Average Survival", ylim = ylim_01)
```

>>>>

```{r yr1-ocean-bxp2, fig.width = p3_width, fig.height = p3_height}
mypar(mfrow = c(1,3), mar = bp_mar, oma = bp_oma)
my_boxplot("sig_Lphi_O0_O1[", ylab = "Process SD", ylim = c(0,2))
my_boxplot(sub_index("kappa_phi_O0_O1[pop]", pop = "."), ylab = "AR(1) Coef.", ylim = c(-1,1)); ref_line(h = 0)
my_boxplot(paste0("rho_Lphi_O0_O1", vcov_inds), ticklabs = vcov_labels, ylab = "Correlation", ylim = c(-1,1)); ref_line(h = 0)
```

@@

### 2023-07-06 03-post-process/output-plots-children/14-known-values.Rmd

  ylim = c(0, max(jags_data$U, na.rm = TRUE))
  known_plot(y_val, label = paste0("Age-", aname, " (", oname, ")"), ylim = ylim)
}

@@

@@

Where `yes` and `no` are vectors storing as elements the number of female carcasses examined in a given return year (`year`) for one population (`one_pop`) that were and were not successful in spawning ("successful" spawning is assigned by the absence of >50% the potential total eggs carried by that female).
Values were bounded on the interval [0.4,1); several years for UGR suggested very low survival with low sample size.

@@

```{r known-phi-Sb-Sa-fn}
# function to make the plot for one population
plot_f = function(j) {
  y_val = jags_data$phi_Sb_Sa[,j]
  y_val[y_val == 0] = NA
  ylim = make_lim(jags_data$phi_Sb_Sa)
  known_plot(y_val, label = pops[j], ylim = ylim)
}

>>>>

  ylim = make_lim(c(0, max(jags_data$U, na.rm = TRUE)))
  known_plot(y_val, label = paste0("Age-", aname, " (", oname, ")"), ylim = ylim)
}

@@

It is possible for the raw data values to suggest >100% of the fish at a given age/origin combo were taken -- the SSM prevents this from happening.

@@

Where `yes` and `no` are vectors storing the number of female carcasses examined each return year (`year`) for one population (`one_pop`) that were and were not successful in spawning ("successful" spawning is assigned by the absence of >50% the potential total eggs carried by that female).
Values were bounded on the interval [0.4,1); several years for UGR suggested very low survival with low sample size.

@@

```{r known-phi-Sb-Sa-fn, fig.width = p4_width, fig.height = p4_height}
# function to make the plot for one population
plot_f = function(j) {
  y_val = jags_data$phi_Sb_Sa[,j]
  y_val[y_val == 0] = NA
  ylim = make_lim(jags_data$phi_Sb_Sa)
  known_plot(y_val, label = pops[j], ylim = ylim)
}
